---
title: "Wine predictor graphical analysis"
author: "AR"
date: "7/29/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(rattle)
data(wine)
```

## Project Assignment Synopsis

### Build web application using Rstudio's shiny package and deploy to shiny server

### Include documentation to describe application

Application must take user input , use that input to perform and output some
analysis

Create a slide presentation to describe the web application (this presentation)

## Approach

This analysis uses the 'wine' data-set which is in the 'rattle' package
The data set describes 178 observations of 13 characteristics of wines which can
be used to predict the 'type' which is a coded response of 3 levels. The data
description is located at https://rdrr.io/cran/rattle.data/man/wine.html

###The web application is published to https://arairkar.shinyapps.io/ddp-week4/


## Web application architecture

### Descriptors: Describe what the application is doing

### Input
Filter the column names from the wine data set except for reponse column1 'Type'
Present list of columns to user for selection

### Output
1. The name of the column selected for analysis
2. A scatter plot with box plots of Type by selected column
3. The subset table of Type and selected column

Note: Ideally, a nominal logistic regression should be performed for 
Type (a discrete response) Vs Selected column ( a numeric factor). This is 
proposed as future work.

## Example output for 'Color' factor

```{r wine, echo=FALSE}
ggplot(wine,aes(y=wine$Color,x=Type,color=Type)) + 
                geom_point() + geom_boxplot(size = 1) + geom_jitter() + 
                coord_flip() + ylab("Color") + xlab("Type")
```